%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Carlos Luna-Peña} \\ \vspace{1pt}
    \small Computer Science @ Texas A\&M University \\ \vspace{1pt}
    \small carlunpen@tamu.edu $|$
    \href{https://github.com/clmoon2}{github.com/clmoon2} $|$
    \href{https://linkedin.com/in/carlunpen}{linkedin.com/in/carlunpen}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in Computer Science; GPA: 3.8/4.0}{May 2026}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Software Engineering, Algorithms, Operating Systems, AI}
        \resumeItem{Completed writing-intensive coursework including specifications, user stories, retrospectives, demos, and peer evaluations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AIPHRODITE}{College Station, TX}
      {Technical Lead \& Full Stack / ML}{Sep. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Led a 6-person team to develop a Next.js and React frontend, integrating real-time outfit recommendations via a FastAPI backend and PostgreSQL, enhancing user engagement.}
        \resumeItem{Architected FastAPI backend serving computer vision embeddings and outfit recommendations to 500+ wardrobe items; reduced query latency by 40\% with optimized PostgreSQL schema.}
        \resumeItem{Developed AI fashion advisor using LangChain and OpenAI, achieving 87\% classification accuracy in clothing tagging, improving user experience and click-through rate by 25\%.}
      \resumeItemListEnd
    \resumeSubheading
      {applyeasy.tech}{College Station, TX}
      {Founder \& Full-Stack Developer}{January 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Founded applyeasy.tech, a SaaS platform automating job applications, reducing manual application time by 75\% through AI-powered role discovery and resume generation.}
        \resumeItem{Built end-to-end job application automation pipeline using n8n, processing 100+ jobs/day, integrating Google APIs for document generation and streamlined email outreach.}
        \resumeItem{Implemented GPT-powered job relevance scoring, leveraging OpenAI API to filter roles based on user qualifications, enhancing user satisfaction and application success rate.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{carlosOS -- Custom Unix Shell} $|$ \emph{C, Linux, Systems Programming}}{October 2024}
      \resumeItemListStart
        \resumeItem{Developed a Unix-style shell with process management, I/O redirection, and pipelines, applying concepts from advanced computer systems coursework.}
        \resumeItem{Implemented custom memory management and process scheduling in C, providing a robust educational operating system environment for testing with QEMU and GDB.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Aggie Events} $|$ \emph{TypeScript, Next.js, React, Node.js, PostgreSQL}}{March 2024}
      \resumeItemListStart
        \resumeItem{Built full-stack event discovery platform with responsive Next.js frontend and PostgreSQL, reducing query latency by 40\% through efficient schema design.}
        \resumeItem{Implemented Google OAuth authentication and secure session management, enhancing user security and experience.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{ApplyEasy Job Automation Engine} $|$ \emph{n8n, OpenAI API, Google APIs, LaTeX}}{February 2025}
      \resumeItemListStart
        \resumeItem{Architected core automation engine orchestrating job scraping, LLM-based filtering, LaTeX resume generation, enabling processing of 100+ job postings daily.}
        \resumeItem{Designed LaTeX resume template system with JSON configuration for seamless PDF compilation and hosting on GitHub.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, JavaScript, C/C++, SQL, Java} \\
             \textbf{Frameworks}{: React.js, Next.js, FastAPI, Node.js, LangChain} \\
             \textbf{Databases \& Tools}{: PostgreSQL, Docker, Git, GitHub Actions, Linux}
    }}
 \end{itemize}

\end{document}