\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge Carlos Luna-Peña} \\ \vspace{1pt}
    \small Computer Science @ Texas A\&M \\ \vspace{1pt}
    \href{mailto:carlunpen@gmail.com}{carlunpen@gmail.com} $|$ 
    \href{https://github.com/clmoon2}{GitHub} $|$ 
    \href{https://linkedin.com/in/carlos-luna}{LinkedIn} $|$ 
    \href{https://applyeasy.tech}{applyeasy.tech} $|$
    College Station, TX
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Texas A\&M University}{College Station, TX}
{Bachelor of Science in Computer Science;  Major GPA: 3.62/4.00}{Aug. 2023 -- Present}
\resumeItemListStart
\resumeItem{Relevant Coursework: Software Engineering, Algorithms, Operating Systems, Artificial Intelligence, Computer Security, Computer Systems, Data Structures.}
\resumeItem{Completed writing-intensive coursework including specifications, user stories, retrospectives, demos, and peer evaluations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{AIPHRODITE}{College Station, TX}
{Technical Lead \& Full Stack / ML}{Sep. 2024 -- Present}
\resumeItemListStart
\resumeItem{Architected FastAPI backend serving computer vision embeddings and outfit recommendations to 500+ wardrobe items; designed PostgreSQL schema with composite indexes reducing query latency by 40\%.}
\resumeItem{Led 6-person engineering team building Next.js/React frontend with Tailwind CSS; integrated real-time outfit recommendations via FastAPI backend and PostgreSQL.}
\resumeItem{Containerized microservices with Docker and configured GitHub Actions CI/CD pipeline for automated testing and deployment.}
\resumeItemListEnd

\resumeSubheading
{applyeasy.tech}{Remote}
{Founder \& Full-Stack / Automation Engineer}{2025}
\resumeItemListStart
\resumeItem{Built end-to-end job application automation pipeline using n8n: scrapes 100+ jobs/day via Apify, filters with OpenAI, generates tailored LaTeX resumes, and sends personalized outreach emails.}
\resumeItem{Founded applyeasy.tech, a SaaS platform automating job applications: role discovery, AI-powered filtering, resume generation, and outreach sequencing—reducing manual application time by 75\%.}
\resumeItem{Integrated Google Workspace APIs (Slides, Sheets, Gmail) for automated document generation and email sequences.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{carlosOS (Educational Operating System)}{C, C++, x86 Assembly, QEMU, Make, GDB}
\resumeItemListStart
\resumeItem{Building educational operating system from scratch in C/C++: bootloader, kernel, process scheduler, and system calls; testing with QEMU and GDB.}
\resumeItem{Implemented Unix-style shell with process management (fork/exec), pipelines (pipe/dup2), and I/O redirection; applied concepts from computer systems coursework.}
\resumeItemListEnd

\resumeProjectHeading
{Aggie Events}{TypeScript, Next.js, React, Tailwind CSS, Node.js, PostgreSQL, Docker, Google OAuth, GitHub Actions}
\resumeItemListStart
\resumeItem{Built full-stack event discovery platform with 8-person team: responsive Next.js frontend, Node.js API, and PostgreSQL database serving campus organizations and students.}
\resumeItem{Extended PostgreSQL schema for events, organizations, and user interactions; added composite indexes reducing p95 query latency by 40\%.}
\resumeItemListEnd

\resumeProjectHeading
{LaTeX Resume Builder \& CLI/Action}{TypeScript, Node.js, LaTeX, GitHub Actions}
\resumeItemListStart
\resumeItem{Developed JSON-to-LaTeX resume generator with TypeScript CLI; compiles structured resume data into ATS-optimized single-page PDFs.}
\resumeItem{Published reusable GitHub Action that automatically builds resume PDFs on push and uploads artifacts; documented integration for developer workflows.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item{
      \textbf{Languages: } TypeScript, Python, JavaScript, C, C++, SQL \\
      \textbf{Frameworks/Libraries: } React.js, Next.js, Node.js, Tailwind CSS, FastAPI \\
      \textbf{Databases: } PostgreSQL, SQLite, Prisma ORM \\
      \textbf{Tools/Platforms: } Docker, GitHub, GitHub Actions, n8n, OpenAI API, Google APIs
    }
  }
\end{itemize}

\end{document}