\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
\textbf{\Large Carlos Luna-Peña} \\
Computer Science @ Texas A\&M \\
\href{mailto:carlunpen@gmail.com}{carlunpen@gmail.com} $|$ \href{https://github.com/clmoon2}{GitHub: clmoon2} $|$ \href{https://linkedin.com/in/carlos-luna}{LinkedIn: carlos-luna} $|$ College Station, TX
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Texas A\&M University}{College Station, TX}
{B.S. in Computer Science; Major GPA: 3.62/4.00}{Aug. 2023 -- Present}
\resumeItemListStart
\resumeItem{Relevant Coursework: Software Engineering, Algorithms, Operating Systems, Artificial Intelligence, Computer Security, Computer Systems.}
\resumeItem{Completed writing-intensive coursework including specifications, user stories, and peer evaluations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{AIPHRODITE (Aggies Create)}{College Station, TX}
{Technical Lead \& Full Stack / ML}{Sep. 2024 -- Present}
\resumeItemListStart
\resumeItem{Architected FastAPI backend serving 500+ wardrobe items with 40\% reduction in query latency using PostgreSQL schema optimization.}
\resumeItem{Developed RAG-powered AI fashion advisor using LangChain/OpenAI improving recommendation CTR by 25\%.}
\resumeItem{Led 6-person team building a responsive Next.js/React frontend, integrating real-time recommendations.}
\resumeItemListEnd

\resumeSubheading
{applyeasy.tech}{Remote}
{Founder \& Full-Stack / Automation Engineer}{2025}
\resumeItemListStart
\resumeItem{Built automation pipeline using n8n, scraping 100+ jobs/day and reducing application time by 75\%.}
\resumeItem{Founded applyeasy.tech, a SaaS platform, leveraging AI for role discovery and resume generation.}
\resumeItem{Designed system for intelligent resume tailoring and personalized email generation using OpenAI API.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{carlosOS (Educational Operating System)}{C, C++, x86 Assembly, QEMU, Make, GDB}
\resumeItemListStart
\resumeItem{Implemented minimal x86 bootloader/kernel with custom management; developed in C/C++ with QEMU.}
\resumeItem{Built Unix-style shell supporting processes and pipelines; applied computer systems concepts.}
\resumeItemListEnd

\resumeProjectHeading
{Aggie Events}{Next.js, React, Tailwind CSS, Node.js, PostgreSQL, Docker}
\resumeItemListStart
\resumeItem{Built event discovery platform with 8-person team, reducing query latency by 40\% using optimized PostgreSQL schema.}
\resumeItem{Implemented Google OAuth, secure session management, and responsive UI components for events.}
\resumeItemListEnd

\resumeProjectHeading
{ApplyEasy Job Automation Engine}{n8n, OpenAI API, Apify, Google APIs, GitHub, LaTeX}
\resumeItemListStart
\resumeItem{Architected automation engine orchestrating job scraping, LLM-based filtering, and resume generation.}
\resumeItem{Designed LaTeX system for PDF compilation, automated via GitHub for reliable document delivery.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}: TypeScript, JavaScript, Python, C, C++, SQL \\
    \textbf{Frameworks/Libraries}: React.js, Next.js, Node.js, Vue.js, Angular, Tailwind CSS \\
    \textbf{Databases}: PostgreSQL, Redis, SQLite \\
    \textbf{Tools/Platforms}: Docker, GitHub Actions, n8n, Apify, CI/CD, OpenAI API, LaTeX
  }}
\end{itemize}

\end{document}